A generalized model for the charge transport properties of dressed quantum Hall systems

### 2021-11-19 response/response.tex

We would like to thank the reviewer for bringing the deficiencies of our manuscript to our attention and providing constructive feedback to improve the quality of our work. We have considered all of your suggestions seriously and revised our manuscript as described below.

\subsubsection*{Comment 1 -
\color{RoyalBlue} My concern is that the manuscript is heavily skewed towards a purely mathematical formulation of the problem. It has a minimal connection to realistic two-dimensional electron systems. The manuscript does not discuss how the results can be applied to understanding mechanisms of charge transport in nanoelectronic devices and can be used to optimize device performance. Without such discussion, the manuscript will have a minimal impact on the community working on developing nanoelectronics.}

We agree that our work has a theoretical bias, and the reader may benefit from some application perspective from our theoretical results to characterize or design nanoelectronic devices. Therefore, we have discussed the physical significance of our theoretical results and their possible use in optimizing nanoelectronic device performance. First, we added a detailed comparison between our theoretical results and experiment observations when no radiation is present.  We also added a new section (Section VII) on this very aspect.

\begin{itemize}
  \item Section VI - third paragraph (page 8):\\
  {\color{Red}
  By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig. 4 are a repetition of the Shubnikov–de Haas(SdH) oscillations.
  As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
  Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
  The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
  The applied gate voltage to the system modifies the Fermi level of the system.
  Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
  This oscillatory behavior against applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
  By comparing these observations against our results in Fig. 4, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
  Furthermore, when we increase the gate voltage, the Fermi level rises. As illustrated in Fig. 4, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78}.
  In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.
  }
  \item Section VII (page 9):\\
  {\color{Red}
  \subsection*{VII. PHYSICAL SIGNIFICANCE OF THE OUTCOMES}

@@

Among the mentioned studies we can identify that experimental work reported in Refs. \cite{zudov01,mani02,zudov03,mani04} are specifically aimed at the unusual oscillations of the magnetoresistance induced by the microwave (millimeter-wave) radiation in 2DEG quantum Hall systems.
These oscillations are known as \textit{microwave-induced resistance oscillations} (MIROs).
To describe these behaviors Durst \textit{et al.} \cite{durst03} introduced a simple theoretical model assuming that the experimentally observed oscillations are a consequence of photoexcited disorder-scattered electrons.
However, later Refs. \cite{dmitriev03,dmitriev05,dmitriev09} proposed a novel model considering the changes were made on
the electron distribution function by the microwave field.

@@

These more generalized models \cite{dmitriev03,dmitriev05,dmitriev09} have successfully described the behavior of MIROs at experimentally relevant temperatures that were missed in the previous model \cite{durst03}.
Furthermore, we can recognize that the underlying mechanism of all these models \cite{durst03,dmitriev03,dmitriev05,dmitriev09} is microwave photon absorption by an electron in the associated system. In our theoretical model, we take into account higher frequencies than microwaves as the dressing electromagnetic field.
Therefore we can identify and quantify significant dissimilarities between our system and MIRO systems \cite{zudov01,mani02,zudov03,mani04,durst03,dmitriev03,dmitriev05,dmitriev09}. They are:

@@

\begin{itemize}
  \item
  the experiments on magnetoresistance oscillations on 2DEG quantum Hall systems \cite{zudov01,mani02,zudov03,mani04} were performed in the microwave frequency range ($30 -\SI{150}{\giga\hertz}$). This leads to building the theoretical models presented in Refs. \cite{durst03,dmitriev03} by assuming that these oscillations are caused by photoexcited electrons. Since these models consider on a relevant frequency range (microwave radiation), it will allow us to acknowledge the photon absorption by electrons. In contrast to that, our consideration is only focused on the systems with high-frequency range dressing fields which will not be associated with any photon absorption.

@@

  \item
  the applied microwave radiation power on the MIRO experiments \cite{mani02,zudov03} varies around the  $\SI{1}{\milli\watt\per\square\centi\metre}$ range. However, in our analysis, we take the dressing field as a high-intensity electromagnetic field, where we cannot consider the dressing field as a perturbation in our analysis. This leads us to recognize the formation of Floquet states together with conventional Landau levels. As we mentioned in our results, we used dressing high-intensity electromagnetic fields of magnitude around the $\SI{100}{\watt\per\square\centi\metre}$ range in our numerical calculations.

@@

  \item
  these fascinating MIROs are only observed under the influence of weak magnetic fields ($B < \SI{0.2}{\tesla}$) in experiments performed in Refs. \cite{zudov01,mani02,zudov03,mani04}. In this range of weak magnetic fields,  we can only observe MIROs as Shubnikov–de Haas (SdH) oscillations reveal only on high-intensity magnetic fields. In comparison to our analysis, we are  interested in the SdH oscillations and manipulation of their characteristics. Therefore in our analysis, we aim at the effects induced by higher intensity magnetic fields ($B \sim \SI{1}{\tesla}$) than the MIRO experiments.

@@

  \item
  in our work, we analyzed the 2DEG quantum Hall system with a dressing high-intensity electromagnetic field which does not contribute to energy exchange between the high-frequency dressing field and electrons. Therefore we have assumed the applied electromagnetic radiation as a pure dressing field. There are two possible absorption mechanisms in a 2DEG quantum Hall system; namely electron transitions between distinct Landau levels and electron transitions between distinct states of the same broadened Landau level. To avoid these absorptions, we have tuned the dressing field into a high-frequency range in our system under the analysis. Furthermore, due to the dressing high-intensity electromagnetic field, the entire electronic states of the conventional 2DEG quantum Hall system will be restructured. We have addressed these modifications through the Floquet theory. However, the MIRO models \cite{durst03,dmitriev03} are based on low-frequency cases where the system can absorb low-frequency photons from the field.

@@

\end{itemize}

Based on the above discussion, we can identify that the high-frequency and low-frequency illumination of 2DEG quantum Hall systems leads to two distinguishable
magneto-transport scenarios.

\begin{itemize}
  \item Section I - fifth paragraph (page 1):\\
  {\color{Red}
  Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIROs) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
  This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
  In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
  The influence induced by a pure dressing field on
  magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
  Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.
  }
  \item Section VI - sixth paragraph (page 9):\\
  {\color{Red}
  Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable
  magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems. However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
  It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field. In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions. This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum Hall systems. Therefore, our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
  }
\end{itemize}

@@

\subsubsection*{Comment 4 -
\color{RoyalBlue} The quantum Quantum Hall effect requires high mobility samples. In these samples, the structure of the disorder is usually complicated and combines both short-length potentials of impurities and long-length electrostatic inhomogeneities. The interplay of these components of disorder opens exciting questions about the transport properties of 2DEGs. What is the structure of disorder considered in the present manuscript and hidden in the notations for Vimp? What are the conditions for validity of eq. (15)?
}

We thank the reviewer for raising this important question. In our previous manuscript, we have presented the detailed derivation of Eq.~[15] with a discussion on models of disorder under Appendix C. However, here we again elucidate our disorder model and approximations made to derive the Eq.~[15] for clarity and to respond to this question.

We modeled the effect caused by impurities in the considered system as a single perturbation potential. Analyzing the electric properties for a specific impurity distribution is a rather formidable task. We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment. Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
We start our analysis by considering a static disorder that corresponds only to elastic electron scattering processes.
We adapt the Edwards model \cite{akkermans10} to represent the randomly distributed impurities over the associated system and we approximate this into a Gaussian white noise.

Since we are presenting the perturbation potential $V(\vb{r})$ by a group of randomly localized impurities, we assume $N_{imp}$ number of identical single impurity potentials distributed randomly but in fixed positions $\vb{r}_i$. Thus, we can describe the perturbation potential $V(\vb{r})$ as the sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$,
\begin{equation} \label{eq:1}
  V(\vb{r}) =
  \sum_{i=1}^{N_{imp}}
  \upsilon (\vb{r}-\vb{r}_i).
\end{equation}
Furthermore, we approximate this perturbation potential as a Gaussian random potential where one can choose the zero of energy such that the potential is zero on average. This model is characterized by the following two equations \cite{akkermans10}
\begin{subequations}
\begin{equation} \label{eq:2}
  \expval{\upsilon(\vb{r})}_{imp} =0,
\end{equation}
\begin{equation} \label{eq:3}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'}),
\end{equation}
\end{subequations}
where $\expval{\cdot}_{imp}$ represents the average over the impurity disorder and $\Upsilon(\vb{r}-\vb{r'})$ is any decaying function that solely depends only on $\vb{r}-\vb{r'}$, and decays with a characteristic length $r_c$. Since this study considers the case where the wavelength of radiation or a scattering electron is much greater than $r_c$, it is reasonable to approximate its two-point correlation function by
\begin{equation} \label{eq:4}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'}),
\end{equation}
where $\Upsilon_{imp}^2$ is a positive constant. A random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can approximately write the total scattering potential as
\begin{equation} \label{eq:5}
  V(\vb{r}) =
  \sum_{i=1}^{N_{imp}}
  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
\end{equation}

Using this expression, we can evaluate the Floquet-Fermi golden rule for a dressed quantum Hall system. Furthermore, considering the properties of a Gaussian white noise impurity distribution \cite{wackerl20,akkermans10}, we assume $V_{imp}$ is a constant in the momentum space.
Here $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
All the detailed steps for the derivation of the Floquet-Fermi golden rule for a dressed quantum Hall system are included in Appendix C.
However, throughout the derivation, we use only the first-order contribution (Born approximation) of the impurity potential.

@@

Since previous studies on Floquet-Drude conductivity \cite{wackerl20}, and magneto-transport properties in undressed \cite{endo09} and dressed \cite{dini16} quantum Hall systems have used this particular Gaussian white noise potential, we also selected this particular impurity model to describe our system. Such a choice enables us to compare our analytical results with these previous models. As you have mentioned in the comment, consideration of other impurity disorder models and their impact on the
magneto-transport properties of dressed quantum Hall system would be an intriguing future research possibility.

Since we have only mentioned the validity conditions we used to derive the Eq.~[15] in Appendix C and not in the main text of the previous manuscript, we have added these validity conditions to the main text of the revised manuscript.

\begin{itemize}
  \item Section IV - first paragraph (page 4):\\
  {\color{Red}
  We have modeled the effect caused by impurities as a single short-range perturbation potential. Analyzing the electric properties for a specific impurity distribution is a rather formidable task. We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
  Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
  Furthermore, we have assumed that a group of randomly distributed impurities forms our perturbation potential under the Edwards impurity model  \cite{akkermans10,wackerl20}.
  Essentially, all these assumptions mean that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20}.
  Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
  Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder. In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential.
  }
\end{itemize}

@@

\subsubsection*{Comment 5 -
\color{RoyalBlue} If continuous illumination is applied to an electron system, the system will heat indefinitely. The distribution function is stabilized when the electron-electron and electron-phonon scattering mechanisms are included. What are the conditions of validity for eqs. (33-34)? The deviations of the distribution function from its equilibrium result in effects that can significantly overcome the equilibrium contributions, see Dmitriev et al, Phys. Rev. B 80, 165327 (2009). However, to capture these effects, a treatment within Floquet-Drude formalism is insufficient and a complete quantum kinetic equation has to be analyzed. Can the authors argue why their results still present some interest to the community even if they potentially disregard more significant contributions?
}

### 2021-11-19 paper/dressed_quantum_hall_response/dressed_quantum_hall_res.tex
Correction to res paper

In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
{\color{Red}
Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIRO) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) fields.
In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
The influence of induced by a pure dressing field on
magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.}
However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
{\color{Red}
The authors of Ref. \cite{dini16} used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.}

@@

The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
However, this theory has not been applied for a dressed quantum Hall system in the previous studies. In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq:14}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
\begin{widetext}
\begin{equation} \label{eq:15}
  \begin{aligned}
    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N = &
    \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N) \\
    & \times
    \int_{-\infty}^{\infty}
    J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
    J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
    \left|
    \int_{-\infty}^{\infty}
    \chi_N \left( \frac{\hbar}{eB}k_2 \right)
    \chi_N \bm{\left(} \frac{\hbar}{eB}
    \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
    dk_2 \right|^2 d k_1,
  \end{aligned}
\end{equation}
\end{widetext}
where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
A more detailed derivation is given in Appendix \ref{appendix_c}.
{\color{Red}
We have modeled the effect caused by impurities as a single short-range perturbation potential. Analyzing the electric properties for a specific impurity distribution is a rather formidable task. We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
Furthermore, we have assumed that a group of randomly distributed impurities forms our perturbation potential under the Edwards impurity model  \cite{akkermans10,wackerl20}.
Essentially, all these assumptions mean that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20},
where $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder. In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential.
}

@@

{\color{Red}
By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of the SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
Therefore, we can identify that many experiments done in low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude for different types of 2DEGs.
The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
Therefore we can achieve the same oscillatory behavior for longitudinal conductivity in a 2DEG quantum Hall system by changing the gate voltage.
The applied gate voltage to the system modifies the Fermi level of the system.
Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation generates SdH oscillations.
This oscillatory behavior with applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
By comparing these observations against our results in Fig.~\ref{fig:4}, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
Furthermore, when we increase the gate voltage, the Fermi level rises. As illustrated in Fig.~\ref{fig:4}, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78}.
In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.}

@@

{\color{Red}
Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable
magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems. However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field. In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions. This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum systems. Therefore our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
}
%===============================================================================

>>>>

In contrast, we can observe more exciting phenomena by simultaneously applying a dressing field to a quantum Hall system already under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, these studies  have not been utilized to describe the optical manipulation of charge transport.
{\color{Red}
Recently, experimental research on the effects of microwave illumination of 2DEG systems revealed microwave-induced resistance oscillations (MIROs) under weak magnetic fields \cite{zudov01,mani02,zudov03,mani04}.
This inspired investigations on the theoretical description of MIROs, and several semiclassical and quantum kinetic equation formalisms have been proposed to address the underlying mechanism of MIROs \cite{durst03,dmitriev03,dmitriev05,dmitriev09}. These formalisms provide a proper explanation for the experimental observations of MIROs. However, these experimental and theoretical works have been linked to photon absorption from low-frequency (microwave) electromagnetic fields.
In contrast to that, high-frequency external illumination on a 2DEG quantum Hall system needs to be studied as a pure dressing (nonabsorbable) field.
The influence induced by a pure dressing field on
magneto-transport properties of 2DEG quantum Hall system needs to be described by a non-absorption mechanism, and it has escaped the researchers’ attention before.
Lately, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall system subjected to a high-frequency field.}
However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system.
{\color{Red}
The authors of Ref. \cite{dini16} used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} \cite{endo09}, those models predict a semi-elliptical broadening against Fermi level for each Landau level and provide less agreement with the empirical results.}

@@

The Floquet-Fermi golden rule was proposed in Ref. \cite{wackerl20} as an approach to analyze the transport properties of dressed quantum systems with impurities.
However, this theory has not been applied for a dressed quantum Hall system in the previous studies. In this analysis, we use Floquet-Fermi golden rule to identify the effects induced by impurities on the magneto-transport properties.
With the help of $t-t'$ formalism \cite{wackerl20,grifoni98,sambe75,peskin93,althorpe97} and applying Floquet states derived in Eq.~(\ref{eq:14}), we can derive an  expression for $(l,l')$-th element of the inverse scattering time matrix for the $N$-th Landau level as
\begin{widetext}
\begin{equation} \label{eq:15}
  \begin{aligned}
    \left(\frac{1}{\tau(\varepsilon,k_x)}\right)^{ll'}_N = &
    \frac{ \pi \hbar\varrho^2}{e^2B^2} \delta(\varepsilon - \varepsilon_N) \\
    & \times
    \int_{-\infty}^{\infty}
    J_l \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
    J_{l'} \bm{\left(} \frac{b\hbar}{eB}({k}_x - k_1) \bm{\right)}
    \left|
    \int_{-\infty}^{\infty}
    \chi_N \left( \frac{\hbar}{eB}k_2 \right)
    \chi_N \bm{\left(} \frac{\hbar}{eB}
    \left( k_1 - {k}_x - k_2 \right) \bm{\right)}
    dk_2 \right|^2 d k_1,
  \end{aligned}
\end{equation}
\end{widetext}
where $\varrho = \eta_{imp} L_x \left[\flatfrac{ V_{imp}}{\pi}\right]^{1/2}$, $\varepsilon$ is a given energy value, $J_l(\cdot)$ are Bessel functions of the first kind with $l$-th integer order, and $\varepsilon_N$ is the energy of the $N$-th Landau level.
A more detailed derivation is given in Appendix \ref{appendix_c}.
{\color{Red}
We have modeled the effect caused by impurities as a single short-range perturbation potential. Analyzing the electric properties for a specific impurity distribution is a rather formidable task. We do not consider a specific impurity distribution here as it is unlikely to represent a measured impurity configuration in an experiment.
Therefore, in this study, we consider the statistically averaged properties of 2DEG over impurity configurations.
Furthermore, we have assumed that a group of randomly distributed impurities forms our perturbation potential under the Edwards impurity model  \cite{akkermans10,wackerl20}.
Essentially, all these assumptions mean that we can write the total scattering potential in the 2DEG as a sum of uncorrelated single impurity potentials $\upsilon(\vb{r})$. This enables us to approximate the impurity potential as a Gaussian white noise \cite{akkermans10,wackerl20}.
Here $\eta_{imp}$ is the number of impurities in a unit area, $V_{imp} = \expval{|V_{{k'}_x,k_x}|^2}_{imp}$ with $V_{{k'}_x,k_x} = \mel**{k'_x}{\upsilon(x) }{k_x}$, and $\braket{x}{k_x} = e^{-ik_x x}$.
Moreover, in this analysis, $\expval{\cdot}_{imp}$ represents the average over the impurity disorder. In this derivation, we only considered the first order (the Born approximation) contribution from the impurity potential.
}

@@

{\color{Red}
By comparing the theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{endo09,wakabayashi78,ochiai190,mancoff96,arapov02,grbic04,caviglia10} studies on the magnetoresistance of 2DEG quantum Hall systems when no radiation is present against our results, we can identify that longitudinal conductivity oscillations in Fig.~\ref{fig:4} are a repetition of the Shubnikov–de Haas(SdH) oscillations.
As observed in the experimental work of Caviglia \textit{et al.} \cite{caviglia10}, the period of SdH oscillations depends only on the perpendicular component of the magnetic field to the plane of the 2DEG.
Therefore, we can identify that many experiments on different types of 2DEGs at low-temperatures \cite{endo09,ochiai190,mancoff96,arapov02,grbic04,caviglia10} have analyzed these SdH oscillations against the applied magnetic field's amplitude.
The cyclotron frequency ($\omega_0$) of the system depends on the magnetic field's perpendicular component to the plane of the 2DEG.
The applied gate voltage to the system modifies the Fermi level of the system.
Since the Landau level energy is only dependent on the cyclotron frequency, this gate voltage variation under a constant magnetic field amplitude generates the same SdH oscillations.
This oscillatory behavior against applied gate voltage has been observed in an  experiment done by Wakabayashi \textit{et al.} \cite{wakabayashi78} in an inversion layer on a silicon surface at low temperature.
By comparing these observations against our results in Fig.~\ref{fig:4}, we can identify that our oscillations also show the same characteristic behavior; i.e  $\hbar\omega_0$ periodic SdH oscillations against the Fermi energy.
Furthermore, when we increase the gate voltage, the Fermi level rises. As illustrated in Fig.~\ref{fig:4}, this will result in a higher conductivity peak value at the higher-order Landau levels. This same behavior was also observed in the experimental observations presented in Ref. \cite{wakabayashi78}.
In our work, we provide analytical results describing the controllability of these conductivity regions using a dressing field.}

@@

{\color{Red}
Lately, several experimental \cite{zudov01,mani02,zudov03,mani04} and theoretical \cite{durst03,dmitriev03,dmitriev05,dmitriev09} studies have uncovered various remarkable
magneto-transport properties induced by microwave radiation on 2DEG quantum Hall systems. However, these experiments and theoretical models only analyzed the behavior of MIROs in 2DEG systems which are based on photon absorption from the applied low-frequency field.
It is important to state that the difference between our SdH oscillations and MIROs \cite{zudov01,mani02,zudov03,mani04} by considering the frequency range of the applied electromagnetic field. In our case, the applied dressing field is in the off-resonant range, and it will only change the broadening of Landau levels, but avoid any contribution towards the photon absorptions. This will clearly describe the crucial difference between low-frequency illumination and high-frequency illumination effects on 2DEG quantum Hall systems. Therefore, our theoretical analysis can help to fill the gap in knowledge of the high-frequency dressing field effects on 2DEG quantum Hall systems.
}
%===============================================================================
